Contextuality and the Born rule in fuzzy quantum theories

### 2017-04-23 prop_letter.tex
prop_letter.tex Add the following new commends...
\newcommand{\mul}{\ensuremath{\mu^{\mathrm{l}}}}
\newcommand{\mur}{\ensuremath{\mu^{\mathrm{r}}}}

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{framed}
\newcommand{\amr}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}\end{framed}}
\newcommand{\yutsung}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}\end{framed}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
\allowdisplaybreaks
\newcommand{\coreBorn}{\mathrm{C}}

@@

Consider a quantum IVPM~$\bar{\mu}$ such that $\boldsymbol{l}:\events\rightarrow\left[0,1\right]$
and $\boldsymbol{r}:\events\rightarrow\left[0,1\right]$ are the left-end
and the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[\boldsymbol{l}\left(E\right),\boldsymbol{r}\left(E\right)\right]$.
This time, when we express the observable~$\mathbf{O}$ as its spectrum
decomposition~$\sum_{i=1}^{N^{-}}\lambda_{i}^{-}P_{i}^{-}+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}P_{i}^{+}$,
we separate the positive and negative eigenvalues and order them from
the smallest to the largest 
\begin{equation}
\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\textrm{ .}
\end{equation}
Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta f\left(P_{i}^{s\prime}\right)=f\left(P_{i}^{s\prime}\right)-f\left(P_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $f\in\left\{ \boldsymbol{l},\boldsymbol{r}\right\} $.
We can combine the classical Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
with Eq.~(\ref{eq:quantum-expectation}) to define the expectation
value of $\mathbf{O}$ with respect to $\bar{\mu}$ as
\begin{eqnarray}
\expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\boldsymbol{l}\left(P_{i}^{+\prime}\right),\Delta\boldsymbol{r}\left(P_{i}^{+\prime}\right)\right]\nonumber \\
 &  & +\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\boldsymbol{l}\left(P_{i}^{-\prime}\right),\Delta\boldsymbol{r}\left(P_{i}^{-\prime}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
\end{eqnarray}
Let $\events'$ denote the set containing $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}$
and satisfies the following conditions.
\begin{itemize}
\item $\mathbb{0}\in\events'$. 
\item $\mathbb{1}\in\events'$. 
\item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
\item For a set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
\end{itemize}
And $\bar{\mu}$ is called convex if for all commuting $P_{0},P_{1}\in\events$,
$\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
Then, the expectation value of an observable with respect to a convex
IVPM is just the minimum and maximum expectation value of the same
observable with respect to its consistent states. Formally speaking,
we have the following theorem.

@@

For example, to compute the expectation value of $\sigma_{\mathrm{z}}=\proj{0}-\proj{1}$
with respect to $\bar{\mu}_{1}$, we have $N^{+}=N^{-}=1$, $\lambda_{1}^{+}=1$,
$\lambda_{1}^{-}=-1$, $P_{1}^{+\prime}=\proj{0}$, $P_{1}^{-\prime}=\proj{1}$,
$P_{2}^{+\prime}=P_{2}^{-\prime}=\mathbb{0}$. Let $\left[\boldsymbol{l}_{1}\left(E\right),\boldsymbol{r}_{1}\left(E\right)\right]=\bar{\mu}_{1}\left(E\right)$,
then $\Delta\boldsymbol{l}_{1}\left(P_{1}^{+\prime}\right)=\boldsymbol{l}_{1}\left(\proj{0}\right)-\boldsymbol{l}_{1}\left(\mathbb{0}\right)=0$,
$\Delta\boldsymbol{l}_{1}\left(P_{1}^{-\prime}\right)=\boldsymbol{l}_{1}\left(\proj{1}\right)-\boldsymbol{l}_{1}\left(\mathbb{0}\right)=0$,
$\Delta\boldsymbol{r}_{1}\left(P_{1}^{+\prime}\right)=\boldsymbol{r}_{1}\left(\proj{0}\right)-\boldsymbol{r}_{1}\left(\mathbb{0}\right)=1$,
$\Delta\boldsymbol{r}_{1}\left(P_{1}^{-\prime}\right)=\boldsymbol{r}_{1}\left(\proj{1}\right)-\boldsymbol{r}_{1}\left(\mathbb{0}\right)=1$.
Therefore, $\expval{\sigma_{\mathrm{z}}}_{\bar{\mu}_{1}}=\left[0,1\right]+\left(-1\right)\left[0,1\right]=\left[-1,1\right]$.

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{framed}
\newcommand{\amr}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}\end{framed}}
\newcommand{\yutsung}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}\end{framed}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
\allowdisplaybreaks
\newcommand{\coreBorn}{\ensuremath{\mathrm{C}}}
\newcommand{\mul}{\ensuremath{\mu^{\mathrm{l}}}}
\newcommand{\mur}{\ensuremath{\mu^{\mathrm{r}}}}

@@

Consider a quantum IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(E\right)=\left[\mul\left(E\right),\mur\left(E\right)\right]$.
This time, when we express the observable~$\mathbf{O}$ as its spectrum
decomposition~$\sum_{i=1}^{N^{-}}\lambda_{i}^{-}P_{i}^{-}+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}P_{i}^{+}$,
we separate the positive and negative eigenvalues and order them from
the smallest to the largest 
\begin{equation}
\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\textrm{ .}
\end{equation}
Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta f\left(P_{i}^{s\prime}\right)=f\left(P_{i}^{s\prime}\right)-f\left(P_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $f\in\left\{ \mul,\mur\right\} $.
We can combine the classical Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
with Eq.~(\ref{eq:quantum-expectation}) to define the expectation
value of $\mathbf{O}$ with respect to $\bar{\mu}$ as
\begin{eqnarray}
\expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]\nonumber \\
 &  & +\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul\left(P_{i}^{-\prime}\right),\Delta\mur\left(P_{i}^{-\prime}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
\end{eqnarray}
Let $\events'$ denote the set containing $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}$
and satisfies the following conditions.
\begin{itemize}
\item $\mathbb{0}\in\events'$. 
\item $\mathbb{1}\in\events'$. 
\item For any projection~$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
\item For a set of mutually orthogonal projections~$\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\events'$,
we have $\sum_{i=1}^{N}P_{i}\in\events'$. 
\end{itemize}
And $\bar{\mu}$ is called convex if for all commuting $P_{0},P_{1}\in\events$,
$\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
Then, the expectation value of an observable with respect to a convex
IVPM is just the minimum and maximum expectation value of the same
observable with respect to its consistent states. Formally speaking,
we have the following theorem.

@@

For example, to compute the expectation value of $\sigma_{\mathrm{z}}=\proj{0}-\proj{1}$
with respect to $\bar{\mu}_{1}$, we have $N^{+}=N^{-}=1$, $\lambda_{1}^{+}=1$,
$\lambda_{1}^{-}=-1$, $P_{1}^{+\prime}=\proj{0}$, $P_{1}^{-\prime}=\proj{1}$,
$P_{2}^{+\prime}=P_{2}^{-\prime}=\mathbb{0}$. Let $\left[\mul_{1}\left(E\right),\mur_{1}\left(E\right)\right]=\bar{\mu}_{1}\left(E\right)$,
then $\Delta\mul_{1}\left(P_{1}^{+\prime}\right)=\mul_{1}\left(\proj{0}\right)-\mul_{1}\left(\mathbb{0}\right)=0$,
$\Delta\mul_{1}\left(P_{1}^{-\prime}\right)=\mul_{1}\left(\proj{1}\right)-\mul_{1}\left(\mathbb{0}\right)=0$,
$\Delta\mur_{1}\left(P_{1}^{+\prime}\right)=\mur_{1}\left(\proj{0}\right)-\mur_{1}\left(\mathbb{0}\right)=1$,
$\Delta\mur_{1}\left(P_{1}^{-\prime}\right)=\mur_{1}\left(\proj{1}\right)-\mur_{1}\left(\mathbb{0}\right)=1$.
Therefore, $\expval{\sigma_{\mathrm{z}}}_{\bar{\mu}_{1}}=\left[0,1\right]+\left(-1\right)\left[0,1\right]=\left[-1,1\right]$.
